%-------------------------
% Resume in LaTeX – updated January 2026
% Author : Javier Hengda Wu Lin
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[utf8]{inputenc}      % ensure UTF-8 encoding
\usepackage[T1]{fontenc}         % ensure proper font encoding for symbols
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=MidnightBlue,urlcolor=MidnightBlue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{noto-sans}

% ---------- color definitions ----------
\definecolor{accent}{HTML}{2563EB}
\definecolor{darktext}{HTML}{1F2937}
\definecolor{lighttext}{HTML}{6B7280}

% ---------- layout tweaks ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pdfgentounicode=1
\setlist[itemize]{leftmargin=0.15in, itemsep=4pt, topsep=3pt}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- section formatting ----------
\titleformat{\section}{
  \vspace{4pt}\color{darktext}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accent}\titlerule \vspace{-2pt}]

% ---------- custom commands ----------
\newcommand{\resumeItem}[1]{\item {\small\color{darktext} #1\vspace{-1pt}}}
\newcommand{\metric}[1]{\textbf{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darktext}#1} & \color{lighttext}#2 \\
      \textit{\small\color{lighttext}#3} & \textit{\small\color{lighttext}#4} \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{darktext}#1} & \textit{\small\color{lighttext}#2} \\
    \end{tabular*}\vspace{-2pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

% -------------------------------------------
%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%
\begin{document}

% ---------- HEADING ----------
\begin{center}
    {\Huge \scshape\color{darktext} Javier Hengda Wu Lin}\\[6pt]
    \small\color{lighttext}
    Barcelona, Spain \,$\cdot$\, +34 617 864 435 \,$\cdot$\,
    \href{mailto:javier.hwulin.devtech@gmail.com}{javier.hwulin.devtech@gmail.com}\\[3pt]
    \href{https://github.com/javierwulin}{GitHub} \,$\cdot$\,
    \href{https://www.linkedin.com/in/JavierHengdaWuLin}{LinkedIn} \,$\cdot$\,
    \href{https://javierhengda.vercel.app/}{Portfolio}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
\small{Backend Software Engineer graduating Dec 2026, seeking SDE Intern roles. Built production-grade APIs on GCP with Spring Boot, Terraform, and Docker. Passionate about distributed systems, clean architecture, and DevOps automation.}

% ---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Barcelona}{Barcelona, Spain}
    {B.Sc.\ Computer Engineering}{Sep 2022 -- Dec 2026}
  \resumeItemListStart
    \resumeItem{Relevant coursework: Distributed Systems, Software Design, Algorithms, Operating Systems, Databases, AI.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- PROJECTS \& RESEARCH ----------
\section{Projects \& Research}
\resumeSubHeadingListStart
\resumeProjectHeading
  {Kofre – Personal \& Social Banking Backend \emph{(Java · Spring Boot · GCP · Terraform · Docker)}}{2025}
\begin{itemize}[leftmargin=0.15in, itemsep=5pt, topsep=3pt]
  \resumeItem{Built \metric{50+ endpoint} RESTful API with Spring Boot 3.5 and Java 21, applying Clean Architecture and DDD for banking ops: accounts, cards, transfers, Bizum, shared expenses.}
  \resumeItem{Automated CI/CD with Cloud Build and Docker multi-stage builds—\metric{sub-3-min deployments} to Cloud Run with zero-downtime rollouts and \metric{0→8 instance} autoscaling.}
  \resumeItem{Codified infrastructure via \metric{5 Terraform modules} (Cloud Run, IAM, VPC, Artifact Registry, Secret Manager), cutting provisioning from hours to \metric{\textless{}10 min}.}
  \resumeItem{Integrated Firestore with repository pattern; enforced quality via JaCoCo, Checkstyle, and Spotless in CI pipeline.}
\end{itemize}

\resumeProjectHeading
  {Battleship – Full-Stack Multiplayer Game \emph{(Python · Django · Vue.js · Pinia · JWT)}}{2025}
\begin{itemize}[leftmargin=0.15in, itemsep=5pt, topsep=3pt]
  \resumeItem{Built real-time multiplayer Battleship with Django REST + Vue.js 3—\metric{4 game phases}, turn-based logic, and session recovery.}
  \resumeItem{Engineered probabilistic AI using hunt/target algorithms for intelligent targeting after successful hits.}
  \resumeItem{Secured API with JWT auth and nested DRF routers; managed state via Pinia for real-time sync across sessions.}
\end{itemize}

\resumeProjectHeading
  {CookBookApp – Recipe Manager \emph{(Java · Android · Firebase)}}{2024}
\begin{itemize}[leftmargin=0.15in, itemsep=5pt, topsep=3pt]
  \resumeItem{Developed Android recipe app with offline-first caching, search, and auth using MVVM + Clean Architecture.}
  \resumeItem{Integrated Firebase Auth and Firestore for real-time sync, supporting \metric{100+ recipes} per user.}
  \resumeItem{Led \metric{4-member} Agile team through \metric{6 sprints}, delivering \metric{95\%} of scoped features on schedule.}
\end{itemize}

\resumeProjectHeading
  {imUB – Media Library Manager \emph{(Java 17 · JavaFX · SQLite)}}{2023}
\begin{itemize}[leftmargin=0.15in, itemsep=5pt, topsep=3pt]
  \resumeItem{Built \metric{30-class} desktop app (\metric{8k+ LOC}) for media library management with live Top-10 rankings.}
  \resumeItem{Applied \metric{4 GoF patterns} (Observer, Factory, Strategy, Singleton) to decouple components and enable real-time UI.}
  \resumeItem{Optimized DAO with batched queries and indexing—\metric{60\% latency reduction} to under \metric{150ms}.}
\end{itemize}

\resumeSubHeadingListEnd

% ---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]
  \small\color{darktext}{
  \item \textbf{Languages:} Java, Python, TypeScript/JavaScript, Go, SQL, C/C++
  \item \textbf{Backend:} Spring Boot, Django, FastAPI, Node.js/Express, REST, GraphQL, gRPC
  \item \textbf{Cloud \& DevOps:} GCP (Cloud Run, Cloud Build, IAM), Docker, Kubernetes, Terraform, GitHub Actions
  \item \textbf{Data:} PostgreSQL, Firestore, MongoDB, Redis, SQLite
  \item \textbf{Testing:} JUnit, PyTest, Mockito, Selenium, JaCoCo, TDD
  \item \textbf{Practices:} Clean Architecture, DDD, Microservices, Design Patterns, CI/CD, Agile/Scrum
  }
\end{itemize}
\vspace{-8pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small\color{darktext}{
  \item \textbf{Spoken:} Spanish (Native), English (Fluent), Chinese (Conversational)
  }
\end{itemize}
% ---------- CERTIFICATIONS ----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeProjectHeading{Mathematics for Machine Learning \emph{(Imperial College London)}}{May 2024}
  \resumeProjectHeading{IBM Data Analyst Professional Certificate}{Apr 2024}
\resumeSubHeadingListEnd

\end{document}
